### 2018-07-06 paper/6-engineering.tex
Final tweaks to Fig. 11

\begin{figure}
\vspace{-2mm}
\begin{subfigure}[b]{0.25\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-build.pdf}}
\caption{Initial build}
\end{subfigure}
\begin{subfigure}[b]{0.40\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-clean.pdf}}
\caption{Clean up and evict \cmd{main.prof}}
\end{subfigure}
\begin{subfigure}[b]{0.31\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-rebuild.pdf}}
\caption{Build \cmd{main.prof} and \cmd{report.txt}}
\end{subfigure}
\vspace{-1mm}
\caption{A Frankenbuild example: (a)~build a human-readable profiling report for
\cmd{main.exe} from information dump \cmd{main.prof} produced by a profiling
tool and record deep constructive traces in the cloud, (b)~remove built files
locally and evict \cmd{main.prof} from the cloud storage, (c)~build
\cmd{main.prof} by executing the profiler (profiling is non-deterministic, hence
the new hash), then build \cmd{report.txt} by downloading it from the matching
deep constructive trace in the cloud, resulting in a Frankenbuild because
\cmd{main.prof} and \cmd{report.txt} are inconsistent. New and evicted cloud
storage entries are highlighted; file hashes are shown in circles.
\label{fig-frankenbuild}}
\vspace{-4mm}
\end{figure}

>>>>

\begin{figure}
\begin{subfigure}[b]{0.32\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-build.pdf}}
\vspace{-1.5mm}
\caption{Initial build}
\end{subfigure}
\begin{subfigure}[b]{0.32\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-clean.pdf}}
\vspace{-1.5mm}
\caption{Clean up and evict \cmd{main.prof}}
\end{subfigure}
\begin{subfigure}[b]{0.34\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-rebuild.pdf}}
\vspace{-1.5mm}
\caption{Build \cmd{main.prof} and \cmd{report.txt}}
\end{subfigure}
\vspace{-1.5mm}
\caption{A Frankenbuild example: (a)~build a human-readable profiling report for
\cmd{main.exe} from information dump \cmd{main.prof} produced by a profiling
tool, then record deep constructive traces in the cloud, (b)~remove built files
locally and evict \cmd{main.prof} from the cloud storage, (c)~build
\cmd{main.prof} by executing the profiler (profiling is non-deterministic, hence
the new hash), then build \cmd{report.txt} by downloading it from the matching
deep constructive trace in the cloud, resulting in a Frankenbuild because
\cmd{main.prof} and \cmd{report.txt} are inconsistent. New and evicted cloud
storage entries are highlighted; file hashes are shown in circles.
\label{fig-frankenbuild}}
\vspace{-4mm}
\end{figure}
